Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2014-01-31 paper/flairs27_AuthorKit/paper.tex
Flairs camera read. Added funding from darpa

Previous approaches are able to find relevant documents given a list of WP
entities as query nodes \cite{mcnamee2012hltcoe}
 \cite{dalton2013bi}\,
\cite{Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
This work involves processing large sets of information to determine which facts may contain references to a WP entity. 
This problem becomes increasingly more difficult when we look to extract relevant facts from
each document.
Each relevant document must now be parsed and processed to determine if a sentence or paragraph is worth being cited.
% Reorder this paragraph
%The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}. Further, this is called streaming because data is being generated as time goes
%on and for each extraction we should only consider current or past data. As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on. Having to balance between infamous and obscure entities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

@@

\begin{figure}
%\hspace{-10mm}
  \centering
%  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
  \includegraphics[width=8.5cm]{./images/System_Diagram_with_model_Vertical-crop.pdf}
% http://convert.neevia.com/pdfconvert/
  %\vspace*{-.1in} 
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
  %\vspace*{-.2in}
\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
%\includegraphics[width=6in]{./images/Pattern.eps}
%\includegraphics[width=6in]{./images/Pattern-eps-converted-to.pdf}
\includegraphics[width = 11cm]{./images/Pattern-crop.pdf}
% cropped pdf created using $ pdfcrop Pattern.pdf
%\vspace*{-.1in}
\caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
entity. The pattern context discovered is `passed away' with a value of `March 2013'. This conforms to type II of our pattern categories.}\label{fig:pattern}
%\vspace*{-.2in}
\end{figure}

@@

\section*{Acknowledgements}
We would like to thank John Frank and NIST for providing the data set.
Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270.

>>>>

Previous approaches are able to find relevant documents given a list of WP
entities as query nodes \cite{mcnamee2012hltcoe,dalton2013bi,Bonnefoy:2013:WDE:2484028.2484180,Balog:2013:CCR:2484028.2484151,ji2011knowledge} 
%,\cite{balog2013cumulative}
.
Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
This work involves processing large sets of information to determine which facts may contain references to a WP entity. 
This problem becomes increasingly more difficult when we look to extract relevant facts from
each document.
Each relevant document must now be parsed and processed to determine if a sentence or paragraph is worth being cited.
% Reorder this paragraph
%The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}. Further, this is called streaming because data is being generated as time goes
%on and for each extraction we should only consider current or past data. As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on. Having to balance between infamous and obscure entities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

@@

\begin{figure}
  \centering
  %\includegraphics{./images/sr.pdf}
  \includegraphics{./images/s_cropped_preview.jpg} % created using adjust size in Mac Preview app.
  \caption{System Architecture.
  Components are logical groups noted with dotted boxes.}
  \label{fig:system}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{./images/pattern-crop_2.jpg}
\caption{Pattern matching for rule evaluation. The slot value is on the right side of the 
entity. The pattern context discovered is `passed away' with a value of `March 2013'. This conforms to type II of our pattern categories.}\label{fig:pattern}
\end{figure}

@@

\section*{Acknowledgements}
We would like to thank John Frank and NIST for providing the data set.
Christan Grant is funded by a National Science Foundation Graduate Research Fellowship under Grant No. DGE-0802270. This work has also been supported in part by DARPA under
FA8750-12-2-0348-2 (DEFT/CUBISM).
